Cover Letter: Replies to Referee

### 2023-11-08 Independence_CH/lessons.tex
LTE at nature; style

Nevertheless, experience  in software engineering is invaluable in
large projects like the present one. For example, it is
(mathematically) misleading when automatic tools (\isa{simp},
\isa{auto}, etc) stop working just because of the sheer size of the
goal (v.g., the same statement with 7 variables succeeds but with 8
variables does not). Scale issues are very easily disregarded in the
abstract but, as a colorful example, the formula $\forceisa({\cdot}0\in 1{\cdot})$
can be explicitly printed by Isabelle2021-1 (it spans nearly 20k symbols), but
$\forceisa({\cdot}\neg{\cdot}\neg{\cdot}0\in 1{\cdot}{\cdot}{\cdot})$
can not.
(For this particular example, one reason for the blow-up in
length comes from the encoding of negation using the “nand”
connective, but otherwise the formulas grow bigger by the sheer
complexity of the definition of the forcing relation.)

>>>>

Nevertheless, experience  in software engineering is invaluable in
large projects like the present one. For example, it is
(mathematically) misleading when automatic tools (\isa{simp},
\isa{auto}, etc) stop working just because of the sheer size of the
goal (v.g., the same statement with 7 variables succeeds but with 8
variables does not). Scale issues are very easily disregarded in the
abstract but, as a colorful example, the formula $\forceisa({\cdot}0\in 1{\cdot})$
can be explicitly printed by Isabelle2021-1 (it spans nearly 20k symbols), but
$\forceisa({\cdot}\neg{\cdot}\neg{\cdot}0\in 1{\cdot}{\cdot}{\cdot})$
can not.
(For this particular example, one reason for the blow-up in
length comes from the encoding of negation using the \isatt{Nand}
connective, but otherwise the formulas grow bigger by the sheer
complexity of the definition of the forcing relation.)
